Quantifying the manageability of pollination networks in an invasion context

### 2017-06-16 paper/manuscript.Rmd
Proceedings B formatting

---
title: "Quantifying the manageability of pollination networks in an invasion context"
classoption: a4paper
csl: ecology-letters.csl
output:
  pdf_document:
    fig_crop: no
    includes:
      after_body: after_body.md
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{tocloft} 
- \usepackage{caption}
- \captionsetup{labelsep=none,textformat=empty}
- \usepackage{lineno}
- \usepackage[nomarkers,tablesfirst, nolists]{endfloat}
- \cftpagenumbersoff{figure}
- \cftpagenumbersoff{table}
documentclass: artikel1
bibliography: references.bib
---

@@

**E. Fernando Cagua^1\*^, Kate L. Wootton^1,2§^, Daniel B. Stouffer^1#^**

@@

^\*^ efc29@uclive.ac.nz 
^§^ kate.l.wootton@gmail.com
^#^ daniel.stouffer@canterbury.ac.nz

* **Running title:** Manageability of pollination networks.

* **Keywords:** Network control, ecological networks, species importance, driver species, food webs, mutualism, management interventions, food web, interaction asymmetry, mutual dependence

* **Article type:** Letter.

* **Number of words:** 148 abstract; approx. 5,006 main text.

* **Number of references:** 65

* **Number of displays:** 5 figures; 1 table.

* **Correspondence to:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand

* **Authorship:** DBS conceived the idea; all authors contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript. All authors contributed to its revision.

* **Data accessibility:** All data used in this manuscript have already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015. The reader should refer to the original sources to access the data.

@@

@@

## Theoretical framework

@@

### Manageability

@@

Note that this framework requires a directed network in which the direction of the links corresponds to the direction of control. 
In the "Empirical application" section below, we explain our approach to determining the link direction in pollination networks.

### Relative importance

@@

## Empirical application

@@

#### Weighting & directing links

@@

#### Statistical analysis

@@

### Relative importance

@@

@@

The authors thank Jane Memmott and coauthors, and eveyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions. 
EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency. 
DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.

>>>>

---
title: "Quantifying the manageability of pollination networks in an invasion context"
classoption: a4paper
csl: proceedings-of-the-royal-society-b.csl
output:
  pdf_document:
    fig_crop: no
    includes:
      after_body: after_body.md
  html_document: default
  word_document: default
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{tocloft} 
- \usepackage{caption}
- \captionsetup{labelsep=none,textformat=empty}
- \usepackage{lineno}
- \usepackage[nomarkers,tablesfirst, nolists]{endfloat}
- \cftpagenumbersoff{figure}
- \cftpagenumbersoff{table}
documentclass: artikel1
bibliography: references.bib
---

@@

**E. Fernando Cagua^1^, Kate L. Wootton^1,2^, Daniel B. Stouffer^1^**

@@

**Author for correspondence:** Daniel Stouffer (daniel.stouffer@canterbury.ac.nz) - +64 3 364 2729 - Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Private Bag 4800, Christchurch 8140, New Zealand

@@

**Keywords:** Network control theory, ecological networks, species importance, driver species, mutualism, management interventions

@@

# Theoretical framework

@@

@@

Note that this framework requires a directed network in which the direction of the links corresponds to the direction of control. 
In the "Methods" section below, we explain our approach to determining the link direction in pollination networks.

@@

@@

### Weighting & directing links

@@

### Statistical analysis

@@

@@

## Data accessibility

All data used in this manuscript have already been published by @Lopezaraiza-Mikel2007, @Bartomeus2008, and @Ballantyne2015. The reader should refer to the original sources to access the data.

## Competing interests

We have no competing interests.

## Author contributions

DBS conceived the idea; all authors contributed to the development of the theoretical framework. EFC performed all analysis. EFC and DBS wrote the manuscript. All authors contributed to its revision.

@@

The authors thank Jane Memmott and coauthors, and eveyone that has made their data available to us, Takeuki Uno for the insight provided to find the set of all maximum matching algorithms, and Jason Tylianakis, Bernat Bramon Mora, Guadalupe Peralta, Rogini Runghen, Warwick Allen, Matthew Hutchinson, and Marilia Gaiarsa for feedback and valuable discussions.

## Funding

EFC acknowledges the support from the University of Canterbury Doctoral Scholarship, the University of Canterbury Meadow Mushrooms Postgraduate Scholarship, a New Zealand International Doctoral Research Scholarship, and a travel grant from the European Space Agency. 
DBS acknowledges the support of a Marsden Fast-Start grant and a Rutherford Discovery Fellowship, administered by the Royal Society of New Zealand.
